---
title: "PDQRnorm"
author: "Sean Finn"
date: "5/19/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggfortify)
library(ggthemes)
library(gridExtra)
```

# Intro
Which values do pnorm, dnorm, qnorm, and rnorm return? How do I remember the difference between these?

I find it helpful to have visual representations of distributions as pictures. It is difficult for me to think of distributions, or differences between probability, density, and quantiles without visualizing the shape of the distribution. So I figured it would be helpful to have a visual guide to pnorm, dnorm, qnorm, and rnorm.


# Prep data

```{r prep data}
# Prep the distribution data
x <- seq(-3, 3, 0.005)
y <- dnorm(x)
normal <- as.data.frame(cbind(x,y))
```


# pnorm

```{r pnorm plot 1}
# pnorm plot 1
# pnorm(0)
x2 <- c(x[1:600], rep(0,601))
y2 <- c(y[1:600], rep(0,601))

p <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "pnorm(0)", x = NULL, y = NULL, 
          subtitle = "P is for Probability") +
     geom_area(inherit.aes = F, mapping = aes(x=x2, y=y2), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -2.6, xmax = -2, ymin = 0.12, ymax = 0.18,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.50", x = -2.3, y = 0.15, size = 6) +
     annotate(geom = "segment", x = -2.7, xend = 0, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p
```

```{r pnorm plot 1.2}
# pnorm plot 1.2
# 1-pnorm(0)
x9 <- c(rep(0,600), x[601:1201])
y9 <- c(rep(0,600), y[601:1201])

p1 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "1-pnorm(0)", x = NULL, y = NULL, 
          subtitle = "P is for Probability") +
     geom_area(inherit.aes = F, mapping = aes(x=x9, y=y9), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = 2.6, xmax = 2, ymin = 0.12, ymax = 0.18,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.50", x = 2.3, y = 0.15, size = 6) +
     annotate(geom = "segment", x = 2.7, xend = 0, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p1
```

```{r pnorm plot 2}
# pnorm plot 2
# pnorm(1)
x3 <- c(x[1:801], rep(1,400))
y3 <- c(y[1:801], rep(0,400))

p2 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 1, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "pnorm(1)", subtitle = "P is for probability", 
          x = NULL, y = NULL) +
     geom_area(inherit.aes = F, mapping = aes(x=x3, y=y3), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -2.6, xmax = -2, ymin = 0.12, ymax = 0.18,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.84", x = -2.3, y = 0.15, size = 6) +
     annotate(geom = "segment", x = -2.7, xend = 1, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p2
```

```{r pnorm plot 3}
# pnorm plot 3
# pnorm(-1)
x4 <- c(x[1:401], rep(-1,800))
y4 <- c(y[1:401], rep(0,800))

p3 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = -1, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "pnorm(-1)", subtitle = "P is for probability", 
          x = NULL, y = NULL) +
     geom_area(inherit.aes = F, mapping = aes(x=x4, y=y4), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -2.6, xmax = -2, ymin = 0.12, ymax = 0.18,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.16", x = -2.3, y = 0.15, size = 6) +
     annotate(geom = "segment", x = -2.7, xend = -1, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p3
```


# dnorm

```{r dnorm plot 1}
# dnorm plot 1
# dnorm(0)

d1 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dnorm(0)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = -3, xmax = -2.4, ymin = 0.33, ymax = 0.39,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.40", x = -2.7, y = 0.36, size = 6) +
     annotate(geom = "segment", y = 0.4, yend = 0.4, x = -3, xend = 0, 
              color = "tomato", size = 1.25, linetype = 6) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
d1
```

```{r dnorm plot 2}
# dnorm plot 2
# dnorm(1)

d2 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 1, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dnorm(1)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = -3, xmax = -2.4, ymin = 0.17, ymax = 0.23,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.24", x = -2.7, y = 0.2, size = 6) +
     annotate(geom = "segment", y = 0.24, yend = 0.24, x = -3, xend = 1, 
              color = "tomato", size = 1.1, linetype = 6) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5),
           plot.subtitle = element_text(face = "italic", hjust = 0.5))
d2
```

```{r dnorm plot 3}
# dnorm plot 3
# dnorm(-1)

d3 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = -1, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dnorm(-1)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = -3, xmax = -2.4, ymin = 0.17, ymax = 0.23,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.24", x = -2.7, y = 0.2, size = 6) +
     annotate(geom = "segment", y = 0.24, yend = 0.24, x = -3, xend = -1, 
              color = "tomato", size = 1.1, linetype = 6) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5),
           plot.subtitle = element_text(face = "italic", hjust = 0.5))
d3
```


# qnorm

```{r qnorm plot 1}
# qnorm plot 1
# qnorm(0.5)

q1 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qnorm(0.5)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x2, y=y2), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -0.25, xmax = 0.25, ymin = 0.03, ymax = 0.09,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0", x = 0, y = 0.06, size = 6) +
     annotate(geom = "segment", x = -2.7, xend = 0, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "text", label = "50%", x = -1.25, y = 0.025, size = 4) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q1
```

```{r qnorm plot 2}
# qnorm plot 2
# qnorm(0.25)
x5 <- c(x[1:466], rep(-0.6745,735))
y5 <- c(y[1:466], rep(0,735))

q2 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = -0.6745, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qnorm(0.25)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x5, y=y5), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -0.3, xmax = 0.3, ymin = 0.03, ymax = 0.09,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "-0.67", x = 0, y = 0.06, size = 5) +
     annotate(geom = "segment", x = -2.7, xend = -0.6745, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "text", label = "25%", x = -1.65, y = 0.025, size = 4) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q2
```

```{r qnorm plot 3}
# qnorm plot 3
# qnorm(0.1)
x6 <- c(x[1:345], rep(-1.28,856))
y6 <- c(y[1:345], rep(0,856))

q3 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = -1.28, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qnorm(0.1)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x6, y=y6), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -0.3, xmax = 0.3, ymin = 0.03, ymax = 0.09,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "-1.28", x = 0, y = 0.06, size = 5) +
     annotate(geom = "segment", x = -2.7, xend = -1.28, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "text", label = "10%", x = -1.85, y = 0.025, size = 4) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q3
```

```{r qnorm plot 4}
# qnorm plot 4
# qnorm(0.75)
x7 <- c(x[1:735], rep(0.6745,466))
y7 <- c(y[1:735], rep(0,466))

q4 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.6745, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qnorm(0.75)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x7, y=y7), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -0.3, xmax = 0.3, ymin = 0.03, ymax = 0.09,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.67", x = 0, y = 0.06, size = 5) +
     annotate(geom = "segment", x = -2.7, xend = 0.6745, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "text", label = "75%", x = -.95, y = 0.025, size = 4) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q4
```

```{r qnorm plot 5}
# qnorm plot 5
# qnorm(0.9)
x8 <- c(x[1:856], rep(1.28,345))
y8 <- c(y[1:856], rep(0,345))

q5 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 1.28, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qnorm(0.9)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x8, y=y8), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = -0.3, xmax = 0.3, ymin = 0.03, ymax = 0.09,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "1.28", x = 0, y = 0.06, size = 5) +
     annotate(geom = "segment", x = -2.7, xend = 1.28, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "text", label = "90%", x = 0.8, y = 0.025, 
              size = 4) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q5
```


# rnorm

```{r rnorm plot}
# rnorm plot
# rnorm(5)

r1 <- ggplot(mapping = aes(x, y), data = normal) +
     geom_line(size = 1.3) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "rnorm(n=5)", subtitle = "R is for Random generation", 
          x = NULL, y = NULL, caption = "Output: c(-1.8, -0.8, 0.1, 0.45, 1.1)") +
     annotate(geom = "segment", y = 0, yend = 0.4, x = 1.1, xend = 1.1,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 0.4, x = 0.45, xend = 0.45,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 0.4, x = -0.8, xend = -0.8,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 0.4, x = 0.1, xend = 0.1,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 0.4, x = -1.8, xend = -1.8,
              color = "blue", linetype = 2) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5)) +
     theme(plot.caption = element_text(face = "bold", size = 14, hjust = 0.5))
r1
```


# save graphs

```{r save graphs}
# pnorm graphs separately
ggsave("~/Desktop/Website materials/pnorm1.png", plot = p, width = 10, height = 6)
ggsave("~/Desktop/Website materials/pnorm2.png", plot = p2, width = 10, height = 6)
ggsave("~/Desktop/Website materials/pnorm3.png", plot = p3, width = 10, height = 6)

# pnorm graphs together
ggsave("~/Desktop/Website materials/pnorm_together.png", 
       arrangeGrob(grobs = list(p3, p, p2), nrow = 1), width = 28, height = 6)

# pnorm (0.5) flipped
ggsave("~/Desktop/Website materials/pnorm_flipped.png", 
       arrangeGrob(grobs = list(p, p1), nrow = 1), width = 20, height = 6)

# dnorm graphs separately
ggsave("~/Desktop/Website materials/dnorm1.png", plot = d1, width = 10, height = 6)
ggsave("~/Desktop/Website materials/dnorm2.png", plot = d2, width = 10, height = 6)
ggsave("~/Desktop/Website materials/dnorm3.png", plot = d3, width = 10, height = 6)

# dnorm graphs together
ggsave("~/Desktop/Website materials/dnorm_together.png", 
       arrangeGrob(grobs = list(d3, d1, d2), nrow = 1), width = 28, height = 6)

# qnorm graphs separately
ggsave("~/Desktop/Website materials/qnorm1.png", plot = q1, width = 10, height = 6)
ggsave("~/Desktop/Website materials/qnorm2.png", plot = q2, width = 10, height = 6)
ggsave("~/Desktop/Website materials/qnorm3.png", plot = q3, width = 10, height = 6)
ggsave("~/Desktop/Website materials/qnorm4.png", plot = q4, width = 10, height = 6)
ggsave("~/Desktop/Website materials/qnorm5.png", plot = q5, width = 10, height = 6)

# qnorm graphs together
ggsave("~/Desktop/Website materials/qnorm_together.png", 
       arrangeGrob(grobs = list(q3, q2, q1, q4, q5), nrow = 1), width = 34, height = 6)

# rnorm graph
ggsave("~/Desktop/Website materials/rnorm.png", plot = r1, width = 10, height = 6)

# example of each type together
ggsave("~/Desktop/Website materials/alltogether.png", 
       arrangeGrob(grobs = list(p, d1, q2, r1), nrow = 2), width = 20, height = 12)
```

