---
title: "uniform distribution visualizations"
author: "Sean Finn"
date: "6/4/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggfortify)
library(ggthemes)
library(gridExtra)
```

# Intro
Which values do punif, dunif, qunif, and runif return? How do I remember the difference between these?

I find it helpful to have visual representations of distributions as pictures. It is difficult for me to think of distributions, or differences between probability, density, and quantiles without visualizing the shape of the distribution. So I figured it would be helpful to have a visual guide to punif, dunif, qunif, and runif.


# Prep data

```{r prep data}
# Prep the distribution data
x <- seq(0, 1, 0.001)
y <- dunif(x)
uniform <- as.data.frame(cbind(x,y))
```


# punif

```{r punif plot 1}
# punif plot 1
# punif(0.5)
x2 <- c(x[1:501], rep(0,500))
y2 <- c(y[1:501], rep(0,500))

p <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.5, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous() +
     labs(title = "punif(0.5)", x = NULL, y = NULL, 
          subtitle = "P is for Probability") +
     geom_area(inherit.aes = F, mapping = aes(x=x2, y=y2), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .39, xmax = .48, ymin = 0.1, ymax = 0.2,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.50", x = 0.435, y = 0.15, size = 6) +
     annotate(geom = "segment", x = 0, xend = 0.5, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p
```

```{r punif plot 1.2}
# punif plot 1.2
# 1-punif(0.5)
x9 <- x
y9 <- c(rep(0,500), y[501:1001])

p1 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.5, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous() +
     labs(title = "1-punif(0.5)", x = NULL, y = NULL, 
          subtitle = "P is for Probability") +
     geom_area(inherit.aes = F, mapping = aes(x=x9, y=y9), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .52, xmax = .61, ymin = 0.1, ymax = 0.2,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.50", x = 0.565, y = 0.15, size = 6) +
     annotate(geom = "segment", x = 1, xend = 0.5, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p1
```

```{r punif plot 2}
# punif plot 2
# punif(0.75)
x3 <- x
y3 <- c(y[1:750], rep(0,251))

p2 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.75, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "punif(0.75)", subtitle = "P is for probability", 
          x = NULL, y = NULL) +
     geom_area(inherit.aes = F, mapping = aes(x=x3, y=y3), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .64, xmax = .73, ymin = 0.1, ymax = 0.2,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.75", x = 0.685, y = 0.15, size = 6) +
     annotate(geom = "segment", x = 0, xend = 0.75, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p2
```

```{r punif plot 3}
# punif plot 3
# punif(0.25)
x4 <- x
y4 <- c(y[1:251], rep(0,750))

p3 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.25, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "punif(0.25)", subtitle = "P is for probability", 
          x = NULL, y = NULL) +
     geom_area(inherit.aes = F, mapping = aes(x=x4, y=y4), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .14, xmax = .23, ymin = 0.1, ymax = 0.2,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.25", x = 0.185, y = 0.15, size = 6) +
     annotate(geom = "segment", x = 0, xend = 0.25, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
p3
```


# dunif

```{r dunif plot 1}
# dunif plot 1
# dunif(0.5)

d1 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.5, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dunif(0.5)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = .39, xmax = .48, ymin = 0.85, ymax = 0.95,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "1.0", x = 0.435, y = 0.9, size = 6) +
     annotate(geom = "segment", y = 1, yend = 1, x = -0.05, xend = 0.5, 
              color = "tomato", size = 1.25, linetype = 1) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
d1
```

```{r dunif plot 2}
# dunif plot 2
# dunif(0.8)

d2 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.8, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dunif(0.8)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = .69, xmax = .78, ymin = 0.85, ymax = 0.95,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "1.0", x = 0.735, y = 0.9, size = 6) +
     annotate(geom = "segment", y = 1, yend = 1, x = -0.05, xend = 0.8, 
              color = "tomato", size = 1.25, linetype = 1) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
d2
```

```{r dunif plot 3}
# dunif plot 3
# dunif(0.2)

d3 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.2, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dunif(0.2)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = .09, xmax = .18, ymin = 0.85, ymax = 0.95,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "1.0", x = 0.135, y = 0.9, size = 6) +
     annotate(geom = "segment", y = 1, yend = 1, x = -0.05, xend = 0.2, 
              color = "tomato", size = 1.25, linetype = 1) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
d3
```

```{r dunif plot 4}
# dunif plot 4
# dunif(1.1)

d4 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 1.11, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "dunif(1.1)", subtitle = "D is for Distribution", 
          x = NULL, y = NULL) +
     annotate(geom = "rect", xmin = 1.01, xmax = 1.1, ymin = 0.85, ymax = 0.95,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.0", x = 1.055, y = 0.9, size = 6) +
     annotate(geom = "segment", y = 1, yend = 1, x = -0.05, xend = 1.11, 
              color = "tomato", size = 1.25, linetype = 1) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
d4
```


# qunif

```{r qunif plot 1}
# qunif plot 1
# qunif(0.5)

q1 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.5, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qunif(0.5)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x2, y=y2), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .39, xmax = .48, ymin = 0.45, ymax = 0.55,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.5", x = 0.435, y = 0.5, size = 6) +
     annotate(geom = "text", label = "50%", x = 0.25, y = 0.05, size = 4) +
     annotate(geom = "segment", x = 0, xend = 0.5, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q1
```

```{r qunif plot 2}
# qunif plot 2
# qunif(0.25)
x5 <- x
y5 <- c(y[1:250], rep(0,751))

q2 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.25, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qunif(0.25)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x5, y=y5), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .14, xmax = .23, ymin = 0.45, ymax = 0.55,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.25", x = 0.185, y = 0.5, size = 6) +
     annotate(geom = "text", label = "25%", x = 0.1, y = 0.05, size = 4) +
     annotate(geom = "segment", x = 0, xend = 0.25, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q2
```

```{r qunif plot 3}
# qunif plot 3
# qunif(0.1)
x6 <- x
y6 <- c(y[1:100], rep(0,901))

q3 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.10, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qunif(0.10)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x6, y=y6), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .12, xmax = .21, ymin = 0.45, ymax = 0.55,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.10", x = 0.165, y = 0.5, size = 6) +
     annotate(geom = "text", label = "10%", x = 0.05, y = 0.05, size = 4) +
     annotate(geom = "segment", x = 0, xend = 0.1, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q3
```

```{r qunif plot 4}
# qunif plot 4
# qunif(0.75)
x7 <- x
y7 <- c(y[1:750], rep(0,251))

q4 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.75, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qunif(0.75)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x7, y=y7), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .64, xmax = .73, ymin = 0.45, ymax = 0.55,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.75", x = 0.685, y = 0.5, size = 6) +
     annotate(geom = "text", label = "75%", x = 0.34, y = 0.05, size = 4) +
     annotate(geom = "segment", x = 0, xend = 0.75, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q4
```

```{r qunif plot 5}
# qunif plot 5
# qunif(0.9)
x8 <- x
y8 <- c(y[1:900], rep(0,101))

q5 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     geom_vline(xintercept = 0.9, color = "blue", size = 1.3, linetype = 2) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "qunif(0.90)", x = NULL, y = NULL, 
          subtitle = "Q is for Quantile") +
     geom_area(inherit.aes = F, mapping = aes(x=x8, y=y8), fill = "tomato", 
               alpha = 0.2) +
     annotate(geom = "rect", xmin = .79, xmax = .88, ymin = 0.45, ymax = 0.55,
              alpha = 1, fill = "white", color = "black") +
     annotate(geom = "text", label = "0.90", x = 0.835, y = 0.5, size = 6) +
     annotate(geom = "text", label = "90%", x = 0.44, y = 0.05, size = 4) +
     annotate(geom = "segment", x = 0, xend = 0.9, y = 0.01, yend = 0.01, 
              size = 1.1, arrow = arrow(length = unit(3, "mm"))) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5))
q5
```


# runif

```{r runif plot}
# runif plot
# runif(5)

r1 <- ggplot(mapping = aes(x, y), data = uniform) +
     geom_line(size = 1.3) +
     scale_x_continuous(n.breaks = 7) +
     labs(title = "runif(n=5)", subtitle = "R is for Random generation", 
          x = NULL, y = NULL, caption = "Output: c(0.68, 0.82, 0.31, 0.73, 0.12)") +
     annotate(geom = "segment", y = 0, yend = 1, x = 0.68, xend = 0.68,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 1, x = 0.82, xend = 0.82,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 1, x = 0.31, xend = 0.31,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 1, x = 0.73, xend = 0.73,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", y = 0, yend = 1, x = 0.12, xend = 0.12,
              color = "blue", linetype = 2) +
     annotate(geom = "segment", x = 0, xend = 0, y = 0, yend = 1, size = 1.1) +
     annotate(geom = "segment", x = 1, xend = 1, y = 0, yend = 1, size = 1.1) +
     theme_classic(base_size = 14, base_family = "Courier") +
     theme(plot.title = element_text(size = 24, face = "bold", hjust = 0.5)) +
     theme(plot.subtitle = element_text(face = "italic", hjust = 0.5)) +
     theme(plot.caption = element_text(face = "bold", size = 14, hjust = 0.5))
r1
```


# save graphs

```{r save graphs}
# punif graphs separately
ggsave("~/Desktop/Website materials/unif graphs/punif1.jpg", plot = p, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/punif2.jpg", plot = p2, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/punif3.jpg", plot = p3, width = 10, height = 6)

# punif graphs together
ggsave("~/Desktop/Website materials/unif graphs/punif_together_horiz.jpg", 
       arrangeGrob(grobs = list(p3, p, p2), nrow = 1), width = 28, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/punif_together_vert.jpg", 
       arrangeGrob(grobs = list(p3, p, p2), nrow = 3), width = 10, height = 18)

# punif (0.5) flipped
ggsave("~/Desktop/Website materials/unif graphs/punif_flipped.jpg", 
       arrangeGrob(grobs = list(p, p1), nrow = 1), width = 20, height = 6)

# dunif graphs separately
ggsave("~/Desktop/Website materials/unif graphs/dunif1.jpg", plot = d1, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/dunif2.jpg", plot = d2, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/dunif3.jpg", plot = d3, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/dunif4.jpg", plot = d4, width = 10, height = 6)

# dunif graphs together
ggsave("~/Desktop/Website materials/unif graphs/dunif_together_horiz.jpg", 
       arrangeGrob(grobs = list(d3, d1, d2), nrow = 1), width = 28, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/dunif_together_vert.jpg", 
       arrangeGrob(grobs = list(d3, d1, d2), nrow = 3), width = 10, height = 18)

# qunif graphs separately
ggsave("~/Desktop/Website materials/unif graphs/qunif1.jpg", plot = q1, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/qunif2.jpg", plot = q2, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/qunif3.jpg", plot = q3, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/qunif4.jpg", plot = q4, width = 10, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/qunif5.jpg", plot = q5, width = 10, height = 6)

# qunif graphs together
ggsave("~/Desktop/Website materials/unif graphs/qunif_together_horiz.jpg", 
       arrangeGrob(grobs = list(q3, q2, q1, q4, q5), nrow = 1), width = 34, height = 6)
ggsave("~/Desktop/Website materials/unif graphs/qunif_together_vert.jpg", 
       arrangeGrob(grobs = list(q3, q2, q1, q4, q5), nrow = 5), width = 10, height = 30)

# runif graph
ggsave("~/Desktop/Website materials/unif graphs/runif.jpg", plot = r1, width = 10, height = 6)

# example of each type together
ggsave("~/Desktop/Website materials/unif graphs/alltogether.jpg", 
       arrangeGrob(grobs = list(p, d1, q2, r1), nrow = 2), width = 20, height = 12)
```

